Continuous Generalization of Buildings \protect\\ by Growing and Merging

### 2017-08-25 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
finished description of simplifying by dilating and eroding

\newcommand{\e}[1]{\times 10^{#1}}
\newcommand{\fig}{Fig.~}
\newcommand{\eq}{Eq.~}
\newcommand{\sect}{Sec.~}

@@

\subsection{Grow based on buffering}
\label{sec:Grow}
We grow building based on buffering. 
There are two typical ways of buffering polygons, i.e.,
one with round joins and the other with miter joins (see 
\fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way because it is 
better at keeping the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}~(a) for an example).
To avoid this kind of interruptions, 
we require that for an angle if a vertex of the 
buffer is more than $\alpha d_\mathrm{G}$, where $d_\mathrm{G}$ is the growing 
distance, away 
from the original vertex, 
a \emph{square} joining is applied
(see \fig\ref{fig:Buffer_MiterLimits}~(b)).
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square joining is applied when an angle is 
smaller than $83.6 \degree$.

@@

\subsection{Merge close buildings by introducing bridges}
The distance between two buildings should be larger than a threshold
\parencite{Regnauld2001,Li2004}.
Following \textcite{Basaraner2008,Stoter2009}, 
we set the separation threshold $\epsilon= 0.2~\text{mm}$ for target map. 
The separation threshold at time $t$ is
\[
d_{\epsilon, t} = \epsilon (S_\mathrm{s}+t(S_\mathrm{g}-S_\mathrm{s})).
\]

@@

\subsection{Simplify grown buildings}
\label{sec:Simplify}
We use a buffering-based method, 
similar to \textcite{Damen2008,Meijers2016}, 
to simplify our grown buildings. 
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes
(see \fig\ref{fig:RemovePitAndSpike}).
At time $t$, we dilate with distance $\dtrm{D}$, 
erode with distance $\dtrm{D}+\dtrm{E}$,
and dilate back with distance $\dtrm{E}$.

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{RemovePitAndSpike}
	\caption{.
	}
	\label{fig:RemovePitAndSpike}
\end{figure}

The buildings have been grown with distance $\dtrm{G}$ 
(see \sect\ref{sec:Grow}).
During the erosion, a part can be eroded with distance 
$\alpha (\dtrm{D}+\dtrm{E})$ at most.
In order not to break a building, the following condition must hold:
\[
\dtrm{G} + \dtrm{D} \ge \alpha (\dtrm{D}+\dtrm{E}),
\]
which means
\[
\dtrm{D} \le \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
\]

@@

The separation threshold at time $t$ is
\[
d_{\epsilon, t} =t \cdot \epsilon S_\mathrm{g}.
\]
One may expect that we define 
$d_{\epsilon, t} = \epsilon (S_\mathrm{s}+t(S_\mathrm{g}-S_\mathrm{s}))$
so that $\epsilon= 0.2~\text{mm}$ holds for a map at any scale.
The reason we do not define it as this way is that 
our growth $\dtrm{G}$ (see \eq\ref{eq:d_Gt}) can be arbitrarily small when $t$ 
is small.
In \sect\ref{sec:Simplify}, the erosion operator requires that

>>>>

\newcommand{\e}[1]{\times 10^{#1}}
\newcommand{\fig}{Fig.~}
\newcommand{\eq}{Eq.~}
\newcommand{\sect}{Sec.~}
\newcommand{\tab}{Tab.~}

%\newcommand{\myeqref}[1]{Eq.~\ref{#1}}
%\newcommand{\mysectref}[1]{Sec.~\ref{#1}}
%\newcommand{\myfigref}[1]{Fig.~\ref{#1}}
%\newcommand{\mytabref}[1]{Tab.~\ref{#1}}

@@

\subsection{Grow based on buffering}
\label{sec:Grow}
We grow building based on buffering. 
There are two typical ways of buffering polygons, i.e.,
one with round joins and the other with miter joins (see 
\fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way because it is 
better at keeping the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}~(a)).
To avoid this kind of interruptions, 
we require that for an angle if a vertex of the 
buffer is more than $\alpha d_\mathrm{G} (\alpha \ge 1)$, 
where $d_\mathrm{G}$ is the growing distance, 
away from the original vertex, 
a \emph{square} joining is applied
(see \fig\ref{fig:Buffer_MiterLimits}~(b)).
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square joining is applied when an angle is 
smaller than $83.6 \degree$.

@@

\subsection{Merge close buildings by introducing bridges}
The distance between two buildings should be larger than a threshold
\parencite{Regnauld2001,Li2004}.
Following \textcite{Basaraner2008,Stoter2009}, 
we set the separation threshold $\epsilon= 0.2~\text{mm}$ for target map. 
The separation threshold at time $t$ is
\begin{equation}
\label{eq:d_epsilont}
d_{\epsilon, t} = \epsilon (S_\mathrm{s}+t(S_\mathrm{g}-S_\mathrm{s})).
\end{equation}

@@

\subsection{Simplify grown buildings}
\label{sec:Simplify}
We use a buffering-based method, 
similar to \textcite{Damen2008,Meijers2016}, 
to simplify our grown buildings. 
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes
(see \fig\ref{fig:RemovePitAndSpike}).

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{RemovePitAndSpike}
	\caption{Remove a pit by dilating and then remove a spike by eroding.
		(a) a polygon with a pit and a spike;
		(b) dilate the polygon in (a) with distance $d$ to remove the pit;
		(c) erode the polygon in (b) with distance $2d$ to remove the spike;
		(d) dilate the polygon in (c) with distance $d$ so that the result has 
		the same size as the polygon in (a).
	}
	\label{fig:RemovePitAndSpike}
\end{figure}

At time $t$, we grow buildings with distance $\dtrm{G}$,
dilate with distance $\dtrm{D} (\dtrm{D}>0)$,
erode with distance $\dtrm{D}+\dtrm{E} (\dtrm{E}>0)$,
and dilate back with distance $\dtrm{E}$.
A problem we may have is that we may break a building by eroding.
The reason is that 
some parts of a building may be increased (by growing and dilating) 
with distance $\dtrm{G}+\dtrm{D}$, 
but be decreased (by eroding) as much as $\alpha (\dtrm{D}+\dtrm{E})$.
If  $\dtrm{G}+\dtrm{D} < \alpha (\dtrm{D}+\dtrm{E})$ 
and a building is not thick enough, 
the building may be broken into several parts
(see \fig\ref{fig:ErosionBreak}).
In order to avoid this problem, we require that
\[
\dtrm{G} + \dtrm{D} \ge \alpha (\dtrm{D}+\dtrm{E}),
\]
which means
\begin{equation}
\label{eq:d_Dt}
\dtrm{D} \le \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
\end{equation}

@@

We would like to use $\dtrm{E}=d_{\epsilon, t}/2$
(see \eq\ref{eq:d_epsilont}) so that
any pits and spikes narrower than $d_{\epsilon, t}$ will be removed.
According to \eq\ref{eq:d_Gt}, $\dtrm{G}$ can be arbitrarily small 
when $t$ is small, 
but $d_{\epsilon, t}$ is at least $\epsilon S_s$. 
In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
which violates \eq\ref{eq:d_Dt}, where $\dtrm{D}>0$.
As a compromise, we use
\[
\dtrm{E} =t \cdot \epsilon S_\mathrm{g}.
\]
Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
$t \cdot \frac{\lambda}{2}\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})-
t \cdot \epsilon S_\mathrm{g} >0$.
As a result, we should make sure that
\begin{equation}
\label{eq:S_g}
S_\mathrm{g} > \frac{\lambda\sqrt{a}}{\lambda\sqrt{a}-2\epsilon} S_s.
\end{equation}

We wish to remove ``bays'' which have ``widths'' less than $2\sqrt{a_h/\pi}$.
\todo{why? more details}
Usually, our $\dtrm{D}$ is not large enough to do so.
We use the upper bound in \eq\ref{eq:d_Dt}, that is,
\[
\dtrm{D} = \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
\]
